Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-13 presentation/paperv2.tex
v2

\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}

>>>>

\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
We noticed that under extreme levels of sparseness from the Matricies generated by CountVectorizer ,
both Logistic Lasso and Logistic Regression would break down, while Multinomial Naive Bayes would produce
usable results. Matricies with a sparseness measure of less than $0.003$ would cause the results for 
Logistic Lasso to deteriorate.
